Adaptive Algorithms Employing Continuous Linear Functionals

### 2018-08-11 AutoAlgorithmLinearFunctionalDataVerC.tex
add contents of examples

\yuhannote{The figure is here in comment} \frednote{The figure looked bad when I compiled it on my screen so I re-ran Matlab and then uploaded the new figures.}
\begin{figure}
	\centering
	\includegraphics[width = 8 cm]{ProgramsImages/SimDirectSolErr.eps}
\end{figure}

>>>>

\begin{figure}[ht]
	\centering
	\begin{tabular}{cc}
		\includegraphics[width =5.5 cm]{ProgramsImages/SimDirectSolAppx.eps} &
		\includegraphics[width = 5.5 cm]{ProgramsImages/SimDirectSolErr.eps}
		\\ (a) & (b)
	\end{tabular}
	\caption{(a) The approximation of the first partial derivative of $f$
		(b) The error of the approximation 
		\label{solfig}} % 
\end{figure}

To do the simulation, we choose the Fourier coefficients $\hf$ to be normal distributed. Let $d=3, a= 2, b=\frac{1}{2},$ and $\varepsilon = 0.1.$ Based on our algorithm, we obtain $ n_{j^\dagger} = 1024.$ Using that, we can obtain the approximated solution and error in Figure \ref{solfig}. Based on Figure \ref{solfig}(b), we can obtain the exact errors are less than $0.01 < \varepsilon $.  This shows our algorithm works.

\begin{figure}[ht]
	\centering
	\begin{tabular}{cc}
		\includegraphics[width = 5.5 cm]{ProgramsImages/SimDirectInpFunAppx.eps}& 
		\includegraphics[width = 5.5 cm]{ProgramsImages/SimDirectInpFunErr.eps}
		\\ (a) & (b)
	\end{tabular}
	\caption{(a) The approximation of the input function $f$
		(b) The error of the approximation 
		\label{inpfig}} % 
\end{figure}

Actually, we can also use these 1024 Fourier coefficients to approximate the input function. The above is the approximation of the input function $f$. Notice that, the errors in Figure \ref{inpfig}(b) are much smaller than the errors in Figure \ref{solfig}(b).
